HTW Model e1

### 2024-03-22 Model/htw_model.qmd
shrink font. remove another hugo file causing a build failure again (migt be due to extra space in date modified).

---
title: HTW Modeling 
author: Thomas Gorman
date:  last-modified #"`r Sys.Date()`"
page-layout: full
categories: [Modeling, ALM, EXAM, R]
lightbox: true
toc: false
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
format:
  html: default
  hugo-md:
    echo: false
    html-math-method: mathjax
    output-file: e1-hugo.md
  gfm:
    echo: true
    output-file: e1-gfm.md
prefer-html: true
---

@@

cId_tr <- c(137, 181, 11)
vId_tr <- c(14, 193, 47)
cId_tt <- c(11, 93, 35)
vId_tt <- c(1,14,74)
cId_new <- c(175, 185, 134, 155, 68, 93, 74)
# filter(id %in% (filter(bestTestEXAM,group_rank<=9, Fit_Method=="Test")

>>>>

---
title: HTW Modeling 
author: Thomas Gorman
date: last-modified #"`r Sys.Date()`"
page-layout: full
categories: [Modeling, ALM, EXAM, R]
lightbox: true
toc: false
format-links: false
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
format:
  html: default
  hugo-md:
    echo: false
    html-math-method: mathjax
    output-file: e1-hugo.md
  gfm:
    echo: true
    output-file: e1-gfm.md
prefer-html: true
---

@@

cId_tr <- c(137, 181, 11)
vId_tr <- c(14, 193, 47)
cId_tt <- c(11, 93, 35)
vId_tt <- c(1,14,74)
cId_new <- c(175, 185, 134, 155, 68, 93, 74, 134)
# filter(id %in% (filter(bestTestEXAM,group_rank<=9, Fit_Method=="Test")

# e3 sbjs - 245, 219, 264, 280, 249, 274

### 2024-03-22 Model/htw_model_e1.qmd
tried remove docusaurus files to see if this fixes the build with jekyll issue failure
shrink font. remove another hugo file causing a build failure again (migt be due to extra space in date modified).

tid1 <- post_dat  |> group_by(id,condit,Model,Fit_Method,x) |> 
  mutate(e2=abs(y-pred)) |> 
  summarise(y1=mean(y), pred1=mean(pred),mean_error=abs(y1-pred1)) |>
  group_by(id,condit,Model,Fit_Method) |> 
  summarise(mean_error=mean(mean_error)) |> 
  arrange(id,condit,Fit_Method) |>
  round_tibble(1)

>>>>

tid1 <- post_dat  |> filter(Fit_Method=="Test_Train") |> group_by(id,condit,Model,Fit_Method) |> 
  mutate(e2=abs(y-pred)) |> 
  summarise(y1=median(y), pred1=median(pred),mean_error=abs(y1-pred1)) |>
  group_by(id,condit,Model,Fit_Method) |> 
  summarise(mean_error=mean(mean_error)) |> 
  arrange(id,condit,Fit_Method) |>
  round_tibble(1)
